Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-02-11 cluster_paper/ms.tex
update paper

%TODO:
%
% n rotation period logs: 2238 % ~/proj/cdips/results/allvariability_reports/NGC_2516/logs
% n all variability reports: 2201 % ~/proj/cdips/results/allvariability_reports/NGC_2516/reports

@@

\newcommand{\nkinematic}{3{,}018\ } % "fullfaint" kinematic sample, core+halo. from any call of earhat.helpers._get_fullfaint_dataframes

@@

%TODO: what are these numbers?
Duly motivated, we collected light curves from TESS photometry
for YYYY of the ZZZZ cluster members.
%TODO write the words to describe the procedure, the detrending, the
%selection function you used for these janky periods, etc.

First, we collected the XXXX Gaia DR2 source\_ids corresponding to the
core and halo members.  For each source, we first retrieved all
available CDIPS light curves, on a per-sector basis.  Then, we
detrended the systematics in each sector individually, and stitched
together the resulting light curves before searching for the
periodicity.  Some details regarding our detrending approach are
discussed in Appendix~\ref{app:detrending}.  After applying a
detrending step aimed at removing systematic trends, we proceeding
with a few small cleaning steps aimed at improving the purity of the
rotation period measurements: we masked 0.7 days at the beginning and
end of each spacecraft orbit, and ran a sliding standard-deviation
rejection window over the light curve, which removed any outlying
points within $\pm3\times$MAD of the median in each window.

>>>>

%TODO:
%
% n rotation period logs: 2238 % ~/proj/cdips/results/allvariability_reports/NGC_2516/logs
% ... which came from ~/Dropbox/proj/cdips/data/cluster_data/cdips_catalog_split/OC_MG_FINAL_v0.4_publishable_CUT_NGC_2516.csv
% n all variability reports: 2201 % ~/proj/cdips/results/allvariability_reports/NGC_2516/reports

@@

\newcommand{\nkinematic}{3{,}018\ } % "fullfaint" kinematic sample, core+halo. from any call of earhat.helpers._get_fullfaint_dataframes
\newcommand{\ncdips}{2,238\ } % e.g., from OC_MG_FINAL_v0.4_publishable_CUT_NGC_2516.csv. checked with plot_target_vs_actual_list_sanity_checks.py

@@

First, we collected the \nkinematic Gaia DR2 source\_ids corresponding to the
kinematically-identified core and halo members.  For each source, we first retrieved all
available CDIPS light curves, on a per-sector basis. 
This yielded
\ncdips light curves, all brighter than $Rp=16$\,mag.
The $Rp=16$\,mag cutoff imposed during the CDIPS processing corresponds
roughly to $(Bp-Rp)_0$ of 2.2, or a spectral type of $\approx$M2V, at
the distance of NGC\,2516.

We cleaned and stitched the light curves as follows.
First, we detrended the systematics in each sector individually, and
stitched together the resulting light curves before searching for the
periodicity.  Some details regarding our detrending approach are
discussed in Appendix~\ref{app:detrending}.  After applying a
detrending step aimed at removing systematic trends, we proceeding
with a few small cleaning steps aimed at improving the purity of the
rotation period measurements: we masked 0.7 days at the beginning and
end of each spacecraft orbit, and ran a sliding standard-deviation
rejection window over the light curve, which removed any outlying
points within $\pm3\times$MAD of the median in each window.
